Exploration

### 2018-03-13 exploration.Rmd
copied IPM image plot axes outside if{ipmPlots}

sample.cells <- sample((1:n.cell)[lam.df$Surv.S>0], nPlots)
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(U$lo, U$hi, length.out=100), size2=size^2, size3=size^3)
  E.t <- xx %>% add_column(s=NA, g=NA, fl=NA, seed=NA)
  xxx <- seq(0, U$hi*.5, length.out=100)
  for(i in sample.cells) {
    z.t <- S$d[[i]][!is.na(S$d[[i]]$size) & S$d[[i]]$yr==tmax,]
    E.t <- sim_expected(E.t, 1:100, 1:100, E.t, p, map(X, ~.[i,]), n_z)
    main.i <- paste("Cell", i)
    w1 <- Re(eigen(U$IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(E.t$size, E.t$s, col=2)
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), ylim=c(U$lo,U$hi),
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(E.t$size, E.t$g, col=2)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(E.t$size, E.t$fl, col=2)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         ylim=range(c(E.t$seed, z.t$seed), na.rm=TRUE),
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(E.t$size, E.t$seed, col=2)
    plot(U$y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    hist(with(S$d[[i]], sizeNext[is.na(size)]), col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red")
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, U$y)
  for(i in sample.cells) {
   z.t <- S$d[[i]][!is.na(S$d[[i]]$size) & S$d[[i]]$yr==tmax,]
   main.i <- paste("Cell", i)
   z.t$y <- U$y[findInterval(z.t$size, U$y, all.inside=T)]
   totSeeds <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
   image.plot(x, x, t(U$Ps[,,i]), main=paste("P matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(sizeNext~size, data=z.t, col=rgb(1,1,1,1/(nrow(z.t)^.25)))
    abline(a=0, b=1, col="white", lty=2)
   image.plot(x, x, t(U$Fs[,,i]), main=paste("F matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*U$hi*.9, col="white")
   image.plot(x, x, t(sens(U$IPMs[,,i])), main=paste("Sensitivity:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
   image.plot(x, x, t(elas(U$IPMs[,,i])), main=paste("Elasticity:", main.i),
              xlab="Size (t)", ylab="Size (t+1)")
   points(sizeNext~size, data=z.t, col=rgb(1,1,1,1/(nrow(z.t)^.25)))
  }
}
image.plot(x, x, t(apply(U$Ps, 1:2, mean)), main="P matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, t(apply(U$Fs, 1:2, mean)), main="F matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, sens(t(apply(U$IPMs, 1:2, mean))), main="Sensitivity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, elas(t(apply(U$IPMs, 1:2, mean))), main="Elasticity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
```

@@

sample.cells <- sample((1:n.cell)[lam.df$Surv.S>0], nPlots)
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(U.f$lo, U.f$hi, length.out=100), 
               size2=size^2, size3=size^3)
  E.t <- xx %>% add_column(s=NA, g=NA, fl=NA, seed=NA)
  xxx <- seq(0, U.f$hi*.5, length.out=100)
  for(i in sample.cells) {
    z.t <- S.f$d[[i]][!is.na(S.f$d[[i]]$size) & S.f$d[[i]]$yr==tmax,]
    E.t <- sim_expected(E.t, 1:100, 1:100, E.t, p.ipm, map(X, ~.[i,]), n_z)
    E.S.t <- sim_expected(E.t, 1:100, 1:100, E.t, p, map(X, ~.[i,]), n_z)
    main.i <- paste("Cell", i)
    w1 <- Re(eigen(U.f$IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    w.S <- Re(eigen(U$IPMs[,,i])$vectors[,1])[-1]; stable.dist.S <- w.S/sum(w.S)
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(E.t$size, E.t$s, col=2); lines(E.S.t$size, E.S.t$s, col=4)
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), ylim=c(U$lo,U$hi),
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(E.t$size, E.t$g, col=2); lines(E.S.t$size, E.S.t$g, col=4)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(E.t$size, E.t$fl, col=2); lines(E.S.t$size, E.S.t$fl, col=4)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         ylim=range(c(E.t$seed, z.t$seed), na.rm=TRUE),
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(E.t$size, E.t$seed, col=2); lines(E.S.t$size, E.S.t$seed, col=4)
    plot(U.f$y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
      lines(U.f$y, stable.dist.S, col=4)
    hist(with(S.f$d[[i]], sizeNext[is.na(size)]), col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p.ipm$rcr_z[1], p.ipm$rcr_z[2]), col=2)
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col=4)
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, U.f$y)
  for(i in sample.cells) {
   z.t <- S.f$d[[i]][!is.na(S.f$d[[i]]$size) & S.f$d[[i]]$yr==tmax,]
   main.i <- paste("Cell", i)
   z.t$y <- U.f$y[findInterval(z.t$size, U.f$y, all.inside=T)]
   totSeeds <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
   image.plot(x, x, t(U.f$Ps[,,i]), main=paste("P matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(sizeNext~size, data=z.t, col=rgb(1,1,1,1/(nrow(z.t)^.25)))
    abline(a=0, b=1, col="white", lty=2)
   image.plot(x, x, t(U.f$Fs[,,i]), main=paste("F matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*U.f$hi*.9, col="white")
   image.plot(x, x, t(sens(U.f$IPMs[,,i])), main=paste("Sensitivity:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
   image.plot(x, x, t(elas(U.f$IPMs[,,i])), main=paste("Elasticity:", main.i),
              xlab="Size (t)", ylab="Size (t+1)")
   points(sizeNext~size, data=z.t, col=rgb(1,1,1,1/(nrow(z.t)^.25)))
  }
}
image.plot(x, x, t(apply(U.f$Ps, 1:2, mean)), main="P matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, t(apply(U.f$Fs, 1:2, mean)), main="F matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, sens(t(apply(U.f$IPMs, 1:2, mean))), main="Sensitivity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, elas(t(apply(U.f$IPMs, 1:2, mean))), main="Elasticity: mean",
           xlab="Size (t)", ylab="Size (t+1)")

>>>>

sample.cells <- sample((1:n.cell)[lam.df$Surv.S>0], nPlots)
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(U$lo, U$hi, length.out=100), size2=size^2, size3=size^3)
  E.t <- xx %>% add_column(s=NA, g=NA, fl=NA, seed=NA)
  xxx <- seq(0, U$hi*.5, length.out=100)
  for(i in sample.cells) {
    z.t <- S$d[[i]][!is.na(S$d[[i]]$size) & S$d[[i]]$yr==tmax,]
    E.t <- sim_expected(E.t, 1:100, 1:100, E.t, p, map(X, ~.[i,]), n_z)
    main.i <- paste("Cell", i)
    w1 <- Re(eigen(U$IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(E.t$size, E.t$s, col=2)
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), ylim=c(U$lo,U$hi),
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(E.t$size, E.t$g, col=2)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(E.t$size, E.t$fl, col=2)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         ylim=range(c(E.t$seed, z.t$seed), na.rm=TRUE),
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(E.t$size, E.t$seed, col=2)
    plot(U$y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
    hist(with(S$d[[i]], sizeNext[is.na(size)]), col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col="red")
  }
}
if(ipmPlots) {
  par(mfrow=c(2,2), mar=c(4,4,2,1))
  x <- c(0, U$y)
  for(i in sample.cells) {
   z.t <- S$d[[i]][!is.na(S$d[[i]]$size) & S$d[[i]]$yr==tmax,]
   main.i <- paste("Cell", i)
   z.t$y <- U$y[findInterval(z.t$size, U$y, all.inside=T)]
   totSeeds <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
   image.plot(x, x, t(U$Ps[,,i]), main=paste("P matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(sizeNext~size, data=z.t, col=rgb(1,1,1,1/(nrow(z.t)^.25)))
    abline(a=0, b=1, col="white", lty=2)
   image.plot(x, x, t(U$Fs[,,i]), main=paste("F matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*U$hi*.9, col="white")
   image.plot(x, x, t(sens(U$IPMs[,,i])), main=paste("Sensitivity:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
   image.plot(x, x, t(elas(U$IPMs[,,i])), main=paste("Elasticity:", main.i),
              xlab="Size (t)", ylab="Size (t+1)")
   points(sizeNext~size, data=z.t, col=rgb(1,1,1,1/(nrow(z.t)^.25)))
  }
}
par(mfrow=c(2,2), mar=c(4,4,2,1))
x <- c(0, U$y)
image.plot(x, x, t(apply(U$Ps, 1:2, mean)), main="P matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, t(apply(U$Fs, 1:2, mean)), main="F matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, sens(t(apply(U$IPMs, 1:2, mean))), main="Sensitivity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, elas(t(apply(U$IPMs, 1:2, mean))), main="Elasticity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
```

@@

sample.cells <- sample((1:n.cell)[lam.df$Surv.S>0], nPlots)
if(regPlots) {
  par(mfrow=c(3,2), mar=c(4,4,2,1))
  xx <- tibble(size=seq(U.f$lo, U.f$hi, length.out=100), 
               size2=size^2, size3=size^3)
  E.t <- xx %>% add_column(s=NA, g=NA, fl=NA, seed=NA)
  xxx <- seq(0, U.f$hi*.5, length.out=100)
  for(i in sample.cells) {
    z.t <- S.f$d[[i]][!is.na(S.f$d[[i]]$size) & S.f$d[[i]]$yr==tmax,]
    E.t <- sim_expected(E.t, 1:100, 1:100, E.t, p.ipm, map(X, ~.[i,]), n_z)
    E.S.t <- sim_expected(E.t, 1:100, 1:100, E.t, p, map(X, ~.[i,]), n_z)
    main.i <- paste("Cell", i)
    w1 <- Re(eigen(U.f$IPMs[,,i])$vectors[,1])[-1]; stable.dist1 <- w1/sum(w1)
    w.S <- Re(eigen(U$IPMs[,,i])$vectors[,1])[-1]; stable.dist.S <- w.S/sum(w.S)
    plot(surv~size, data=z.t, ylim=c(0,1), pch=20, col=rgb(0,0,0,0.2),
         main=paste("Surv:", main.i), xlab="Size (t)", ylab="P(surv to t+1)")
      lines(E.t$size, E.t$s, col=2); lines(E.S.t$size, E.S.t$s, col=4)
    plot(sizeNext~size, data=z.t, pch=20, col=rgb(0,0,0,0.2), ylim=c(U$lo,U$hi),
         main=paste("Growth:", main.i), xlab="Size (t)", ylab="Size (t+1)")
      lines(E.t$size, E.t$g, col=2); lines(E.S.t$size, E.S.t$g, col=4)
      abline(a=0, b=1, lty=2)
    plot(fl~size, data=z.t, pch=20, ylim=c(0,1), col=rgb(0,0,0,0.2),
         main=paste("P(Flower):", main.i), xlab="Size (t)", ylab="P(flower)")
      lines(E.t$size, E.t$fl, col=2); lines(E.S.t$size, E.S.t$fl, col=4)
    plot(seed~size, data=z.t, pch=23-z.t$fl*3, col=rgb(0,0,0,0.2), 
         ylim=range(c(E.t$seed, z.t$seed), na.rm=TRUE),
         main=paste("nSeeds:", main.i), xlab="Size (t)", ylab="Number of seeds")
      lines(E.t$size, E.t$seed, col=2); lines(E.S.t$size, E.S.t$seed, col=4)
    plot(U.f$y, stable.dist1, ylab="", type="l", col=2, 
         main=paste("Stable size distribution:", main.i), xlab="Size (t)")
      lines(U.f$y, stable.dist.S, col=4)
    hist(with(S.f$d[[i]], sizeNext[is.na(size)]), col="grey", freq=F, 
         main=paste("Recruit sizes:", main.i), xlab="Recruit size (t+1)")
      lines(xxx, dnorm(xxx, p.ipm$rcr_z[1], p.ipm$rcr_z[2]), col=2)
      lines(xxx, dnorm(xxx, p$rcr_z[1], p$rcr_z[2]), col=4)
  }
}
if(ipmPlots) {
  for(i in sample.cells) {
   z.t <- S.f$d[[i]][!is.na(S.f$d[[i]]$size) & S.f$d[[i]]$yr==tmax,]
   main.i <- paste("Cell", i)
   z.t$y <- U.f$y[findInterval(z.t$size, U.f$y, all.inside=T)]
   totSeeds <- group_by(z.t, y) %>% summarise(seed=sum(seed, na.rm=T))
   image.plot(x, x, t(U.f$Ps[,,i]), main=paste("P matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(sizeNext~size, data=z.t, col=rgb(1,1,1,1/(nrow(z.t)^.25)))
    abline(a=0, b=1, col="white", lty=2)
   image.plot(x, x, t(U.f$Fs[,,i]), main=paste("F matrix:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
    points(totSeeds$y, totSeeds$seed/max(totSeeds$seed)*U.f$hi*.9, col="white")
   image.plot(x, x, t(sens(U.f$IPMs[,,i])), main=paste("Sensitivity:", main.i), 
              xlab="Size (t)", ylab="Size (t+1)")
   image.plot(x, x, t(elas(U.f$IPMs[,,i])), main=paste("Elasticity:", main.i),
              xlab="Size (t)", ylab="Size (t+1)")
   points(sizeNext~size, data=z.t, col=rgb(1,1,1,1/(nrow(z.t)^.25)))
  }
}
par(mfrow=c(2,2), mar=c(4,4,2,1))
x <- c(0, U.f$y)
image.plot(x, x, t(apply(U.f$Ps, 1:2, mean)), main="P matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, t(apply(U.f$Fs, 1:2, mean)), main="F matrix: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, sens(t(apply(U.f$IPMs, 1:2, mean))), main="Sensitivity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
image.plot(x, x, elas(t(apply(U.f$IPMs, 1:2, mean))), main="Elasticity: mean",
           xlab="Size (t)", ylab="Size (t+1)")
